---
title: "KF Report Compiler"
output: html_document
runtime: shiny
---

```{r options, echo=FALSE}
library(knitr)
opts_chunk$set(warning=FALSE, message=FALSE, echo=FALSE, fig.width=10)
options(rcharts.mode = 'iframe', rcharts.cdn = TRUE)
knitr::opts_chunk$set(results = "asis", comment = NA)
```

```{r init}
source("lib/kf-api-lib.R") # load the function library
source("utils/utils.R") # Load utility functions

library(ggplot2)
library(lattice)
library(rCharts)
library(ggthemes)
library(tm)
suppressMessages(library(dplyr))
suppressMessages(require(shinyIncubator))

## Login info
# host = "http://132.203.154.41:8080/kforum/"
host = "http://kf.utoronto.ca:8080/kforum/"
username = "bodong" # YOUR_USERNAME
password = "19868873" # YOUR_PASSWORD

## Create a curl handle that will be shared among API calls
curl = CreateCurlHandle()

## 1. User authentication
regs = Authenticate(host, username, password, curl)
# regs[, c("sectionId", "sectionTitle")] # check sections I'm in

## Choose a section/community I'm interested in
userId = regs$authorInfo.guid[1]
sectionId = regs$sectionId[1]

communityInfo = SelectCommunity(host, regs[1, "guid"], curl) # Notify the server; IMPORTANT

## Do user control here
if(communityInfo$userRole == "Manager") {
  
}
```

```{r dataprep}
# all posts in the community
posts <- tbl_df(GetSectionPosts(host, sectionId, curl))

# all views
views = tbl_df(GetSectionViews(host, sectionId, curl))

# all authors
authors = tbl_df(GetAllAuthors(host, sectionId, curl))

# logs
logs = tbl_df(GetLogs(host, views$guid, curl))

# promising ids
pIdeaIds = unlist(sapply(posts$promisingIdeas, function(df)
  return(df$guid)
))

scaffolds <- unlist(sapply(posts$body, function(x) {
  r <- regexpr("class=\"startLabelTag\">(.*?)</span>", x)
  m <- regmatches(x, r)
  gsub("class=\"startLabelTag\">|</span>", "", m)
}))

now = Sys.time()
```

## `r communityInfo$section$title`

### Basic Information

- `r nrow(authors)` authors
- `r nrow(posts)` notes
- `r length(pIdeaIds)` promising ideas
- `r sum(CountWords(posts$body_text))` words


## Community Activities

__Posts__

```{r}
getPostTimeseries = reactive({
  days = input$days
  
  fromDate = as.POSIXlt(round(now, "hour") - days * 3600 * 24)
  posts$date = strptime(posts$created, "%b %d, %Y %I:%M:%S %p")
  posts = posts[posts$date >= fromDate, ]
  
  if(days == 1) { ## in the past 24 hours, split by hours
    posts$offset = as.integer(difftime(posts$date, fromDate, units="hours"))
    
    select(posts, guid, offset) %>% 
      group_by(offset) %>%
      summarise(count = n()) %>%
      arrange(offset)
  
  } else {
    posts$date = as.Date(round(strptime(posts$created, "%b %d, %Y %I:%M:%S %p"), "days"))
    group_by(posts, date) %>%
      summarise(count = n()) %>%
      arrange(date)
    }
  })

inputPanel(
  sliderInput("days", 
              "Number of Days:", 
               value = 7,
               min = 1, 
               max = 120)
)

renderPlot({
  
  ts = getPostTimeseries()
  if(input$days == 1) {
    ggplot(data=ts, aes(x = offset, y = count)) +
      geom_bar(stat="identity") + 
      scale_x_continuous(breaks=seq(0, 24, 1), limits=c(0, 25)) + 
      xlab("Hour") + theme_bw()
  } else {
    ggplot(data=ts, aes(x = date, y = count)) +
      geom_bar(stat="identity", width = .3) + 
      #scale_x_discrete(limits = c(min(ts$date)-1, max(ts$date)+1)) + 
      xlab("Date") + theme_bw()
  }
})
```

__Scaffolds__

```{r scaffolds, results = 'asis', comment = NA}
tmp = data.frame(table(scaffolds))
tmp = tmp[with(tmp, order(-Freq)), ]
tmp <- within(tmp, 
              scaffolds <- factor(scaffolds, 
                                  levels=rev(as.character(scaffolds))))

renderPlot({
  ggplot(data=tmp, aes(x = scaffolds, y = Freq)) +
    geom_bar(stat = "identity") +
    coord_flip() + theme_bw()
})
```


__Social network__

```{r sna}

getReadLogs = function() {
  primaryAuthorIds <- posts$primaryAuthorId
  names(primaryAuthorIds) = unique(posts$guid)
  authornames <- authors$userName
  names(authornames) = unique(authors$guid)
  #print(logs)
  
  readlogs = subset(logs, operationType=="READ" & entityType=="POST")
  data.frame("from"=readlogs$userName, 
             "to"=authornames[primaryAuthorIds[readlogs$entityId]], 
             timestamp=kf.sna.time(readlogs$accessTime))
}


rmarkdown::render_delayed({
  renderPlot({
    readlogs = getReadLogs()
    snaData = data.frame("source"=readlogs$from, "target"=readlogs$to)
    library(igraph)
    g <- graph.data.frame(snaData, directed=TRUE)
    plot(g, layout=layout.kamada.kawai,
         vertex.size=15, vertex.label.color="black", vertex.color="red",
         edge.arrow.size=0.5, edge.curved=F)
    })
  })
```


## Individuals

Summary table


Interactive table:
row: students
col: counts (notes written, words written, notes read)
control: in the past day, week, month, ... + sort by ? (provided in table?)

Interactive table: weekly activity
similar but by week

### Impact Analysis

Interactive table:

- Notes written
- Promising ideas given
- PI received
- PI ratio
- Build on given
- Build on received
- Build on ratio
- Reference??

## Custom report

[Custom Report](kf-custom-report.Rmd)

This R Markdown document is made interactive using Shiny. Unlike the more traditional workflow of creating static reports, you can now create documents that allow your readers to change the assumptions underlying your analysis and see the results immediately. 

To learn more, see [Interactive Documents](http://rmarkdown.rstudio.com/authoring_shiny.html).

## Inputs and Outputs

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change.  This demonstrates how a standard R plot can be made interactive by wrapping it in the Shiny `renderPlot` function. The `selectInput` and `sliderInput` functions create the input widgets used to drive the plot.

```{r, echo=FALSE}
inputPanel(
  selectInput("n_breaks", label = "Number of bins:",
              choices = c(10, 20, 35, 50), selected = 20),
  
  sliderInput("bw_adjust", label = "Bandwidth adjustment:",
              min = 0.2, max = 2, value = 1, step = 0.2)
)

renderPlot({
  hist(faithful$eruptions, probability = TRUE, breaks = as.numeric(input$n_breaks),
       xlab = "Duration (minutes)", main = "Geyser eruption duration")
  
  dens <- density(faithful$eruptions, adjust = input$bw_adjust)
  lines(dens, col = "blue")
})
```

## Embedded Application

It's also possible to embed an entire Shiny application within an R Markdown document using the `shinyAppDir` function. This example embeds a Shiny application located in another directory:

```{r, echo=FALSE}
shinyAppDir(
  system.file("examples/06_tabsets", package="shiny"),
  options=list(
    width="100%", height=550
  )
)
```

Note the use of the `height` parameter to determine how much vertical space the embedded application should occupy.

You can also use the `shinyApp` function to define an application inline rather then in an external directory.

In all of R code chunks above the `echo = FALSE` attribute is used. This is to prevent the R code within the chunk from rendering in the document alongside the Shiny components.



