Minimal example of using KF APIs in R
========================================================

```{r, echo=FALSE}
library(knitr)
opts_chunk$set(warning=FALSE, message=FALSE, fig.width=10)
```

```{r}
source("lib/kf-api-lib.R") # load the function library

library(ggplot2)
library(ggthemes)
library(tm)
suppressMessages(library(dplyr))

## Login info
host = "http://132.203.154.41:8080/kforum/"
# host = "http://kf.utoronto.ca:8080/kforum/"
username = "bodong" # YOUR_USERNAME
password = "000000" # YOUR_PASSWORD

## Create a curl handle that will be shared among API calls
curl = CreateCurlHandle()
```

## 1. User authentication

```{r}
## 1. User authentication
regs = Authenticate(host, username, password, curl)
regs[, c("sectionId", "sectionTitle")] # check sections I'm in

# http://132.203.154.41:8080/kforum/kfsection.xhtml#kfview;registered=6a0fb6e6-8ed0-42cc-9320-ebab4e7b0d40;view=76875f36-0d24-458c-ab6d-12f0c6e9bebf

## Choose a section/community I'm interested in
userId = regs$authorInfo.guid[1]
sectionId = regs$sectionId[1]

(communityInfo = SelectCommunity(host, regs[1, "guid"], curl)) # Notify the server; IMPORTANT
```

## 2. My posts

```{r}
## 2. My posts
posts = tbl_df(GetSectionPosts(host, sectionId, curl))
glimpse(posts)
myPosts = FilterPostsByAuthors(posts, userId) # all my posts here
# str(myPosts[1, ])
```

### 2.1. Compare number of my posts with the community average

```{r}
# 2.1. Compare number of my posts with the community average
authors = do.call("rbind", posts$authors) # all unique authors
tmp = data.frame(author=factor(c("Me","Average"), levels=c("Me","Average")),
                 notes=c(nrow(myPosts), nrow(posts)/length(unique(authors$guid))))
ggplot(data=tmp, aes(x=author, y=notes, fill=author)) +
  geom_bar(colour="black", stat="identity") + 
  ggtitle("Number of my posts compared to community average") + 
  guides(fill=FALSE) + 
  theme_solarized()
```

### 2.2. My posting calendar

```{r}
# 2.2. My posting calendar
dates = strptime(myPosts$created, "%b %d, %Y %I:%M:%S %p")
dates_str = as.character(format(dates, format="%Y-%m-%d"))
tmp = data.frame(table(dates_str))
names(tmp) = c("date", "value")
CalendarHeatmap(tmp, title="Posting Activities")
```

# 2.3. My top terms

```{r, results='hide'}
# 2.3. My top terms
myNotes = Corpus(VectorSource(myPosts$body_text))
myDtm <- DocumentTermMatrix(myNotes, control = list(
  #   stemming = TRUE, 
  stopwords = TRUE, minWordLength = 3, 
  removeNumbers = TRUE, removePunctuation = TRUE))
myFreqTerms = findFreqTerms(myDtm, 8, 100)
myFreq = colSums(inspect(myDtm[, myFreqTerms]))
```

```{r}
tmp = sort(myFreq, decreasing=TRUE)
data.frame(term=names(tmp), freq=tmp, row.names=NULL)
```


## 3. Views in my community

```{r}
## 3. Views in my community
views = tbl_df(GetSectionViews(host, sectionId, curl))
glimpse(views)
# str(views[1, ])
views$title # view titles
```

## 4. Inspect one view

```{r}
## 4. Inspect one view
viewId = views[2, "guid"] # I'm interested in view #15
view = GetView(host, viewId, curl)
```

### 4.1. Number of posts in the view

```{r}
# 4.1. Number of posts in the view
nrow(view$viewPostRefs)
```

### 4.2. Percentage of build-ons posts

```{r}
paste0(round(100 * nrow(view$buildOns) / nrow(view$viewPostRefs), 2), "%")
```


### 4.2. Revisualize the view

```{r}
# 4.2. Revisualize the view
ggplot(view$viewPostRefs, aes(x=location.point.x, y=location.point.y)) + 
  geom_text(aes(label=postInfo.title), hjust=0) + 
  ggtitle(view$title) + 
  scale_y_reverse() + theme_bw() + 
  theme(axis.title=element_blank(), 
        axis.text=element_blank(),
        axis.ticks=element_blank(), 
        panel.grid=element_blank())
```

### 4.3. Top terms in the view

```{r, results='hide'}
# 4.3. Top terms in the view
notes = Corpus(VectorSource(view$viewPostRefs$postInfo.body_text))
dtm <- DocumentTermMatrix(notes, control = list(
  stopwords = TRUE, minWordLength = 3, 
  removeNumbers = TRUE, removePunctuation = TRUE))
freqTerms = findFreqTerms(dtm, 8, 100)
freq = colSums(inspect(dtm[, freqTerms]))
```

```{r}
tmp = sort(freq, decreasing=TRUE)
data.frame(term=names(tmp), freq=tmp, row.names=NULL)

# overlap between my freq terms and shared freq terms
intersect(myFreqTerms, freqTerms)
```

## SNA

```{r}
viewIds = views$guid[14]
# viewIds = head(views$guid)
logs = GetLogs(host, viewIds, curl)
authors = GetAllAuthors(host, sectionId, curl)
    
primaryAuthorIds <- posts$primaryAuthorId
names(primaryAuthorIds) = posts$guid
authornames <- authors$userName
names(authornames) = authors$guid

readlogs = subset(logs, operationType=="READ" & entityType=="POST")
readlogs = tbl_df(data.frame("from"=readlogs$userName, 
                      "to"=authornames[primaryAuthorIds[readlogs$entityId]], 
                      timestamp=kf.sna.time(readlogs$accessTime)))

library(igraph)
df <- data.frame("source"=readlogs$from, "target"=readlogs$to)
g <- graph.data.frame(df, directed=TRUE)
plot(g, layout=layout.circle, 
     vertex.size=15, vertex.label.color="black", vertex.color="red", 
     edge.arrow.size=0.5, edge.curved=F)
```

## Personal collaboration

### Who are reading me?

TODO: Get the top 5 people who are reading my notes. Results should be presented as a table, with two columns - one is their first name, and the other is the count. The table should be sorted by the count, and then the name.

Hint: `userId` decides the current author; use `GetLogs(host, viewIds, curl)` above (in SNA) to get reading log; then find out the top readers. Note: It's okay to restrict the search in one view.

```{r}
# myName = communityInfo$currentAuthor$userName # get my username
myName = "ymatsuzawa" # just for testing
readlogs %>%
  filter(to == myName) %>%
  group_by(from) %>%
  summarise(count = n()) %>%
  arrange(desc(count))
```

### Whom am I reading?

Similar as above.

```{r}
readlogs %>%
  filter(from == myName) %>%
  group_by(to) %>%
  summarise(count = n()) %>%
  arrange(desc(count))
```


### Whom am I building on?

TODO: Get the top 5 people who are building on my notes. Results should be similar to the above.

This might be more complicated.

```{r}
# get all views
viewIds = views$guid
library(plyr)

# get buildon links in all views
buildons = laply(viewIds, function(id) {
  print(id)
  view = GetView(host, id, curl)
  buildons = view$buildOns
  if(length(buildons) == 0)
    return(NULL)
  posts = view$viewPostRefs[, c("guid", "postInfo.guid")]
  buildons$built.ids = laply(buildons$built, function(x) {
    posts$postInfo.guid[which(posts$guid == x)[1]]
  })
  buildons$buildsOn.ids = laply(buildons$buildsOn, function(x) {
    posts$postInfo.guid[which(posts$guid == x)[1]]
  })
  return(buildons)
})
# buildons = do.call("rbind", buildons)

# link/replace note ids with their primary author ids
buildons$from = authornames[primaryAuthorIds[buildons$buildsOn.ids]]
buildons$to = authornames[primaryAuthorIds[buildons$built.ids]]

# count and summarize
buildons %>%
  select(from, to) %>%
  filter(from == myName) %>%
  group_by(to) %>%
  dplyr::summarise(count = n()) %>% # mask the summarise function 
  arrange(desc(count))
```


### Who are building on me?

```{r}
buildons %>%
  select(from, to) %>%
  filter(to == myName) %>%
  group_by(from) %>%
  dplyr::summarise(link_count = n()) %>%
  arrange(desc(link_count))
```
